Pyg4ometry: a python library for the creation of Monte Carlo particle transport physical geometries

### 2019-08-11 public/paper/pyg4ometry.tex
Transform maths in paper
Updated gdml tag and class table

\subsection{Geant Detector Mark-up Language} 
To exchange geometry descriptions Geant Detector Mark-up Language (GDML) was developed. Geant4 and ROOT can read and write GDML format and it is commonly
used as an exchange format for Geant4 geometries. 
\begin{table}[hbt!]
\centering
\begin{tabular}{|c|c|c|} \hline
GDML tag 		&  Child tags				& pyg4ometry class 			\\ \hline
Defines 			&						&						\\
Solids 			&						&						\\
Materials 			&						&						\\
Structure			&						&						\\ \hline
\end{tabular}
\caption{GDML tags and corresponding {\it pyg4ometry} classes.}
\end{table}

\section{{\em pyg4ometry} design and layout}
The core of {\em pyg4ometry} consists of python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
The constructors of the python classes are kept as close to the original Geant4 C++ implementation so that {\it pyg4ometry} users do not have to learn 
a new API. Geometry construction in python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
should be able to start creating geometry in pyg4ometry immediately. In the following sections novel or important developments in {\it pyg4ometry} are described.

@@

\subsection{Visualisation}
A  geometry hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 volume hierarchy is sufficient 
to place the meshes associated with each physical volume. The python version of Geant4's physical volume is also used to store visualisation attributes like the solids 
color, surface or wireframe representation and visibility. Overlaps detected in the discretised mesh geometry can be displayed separately to allow a user to remove
the potential overlaps. This is dependent on the accuracy of the mesh generated and is a particular problem with meshes based on curved surfaces.

>>>>

\subsection{Geant Detector Mark-up Language} 
To exchange geometry descriptions Geant Detector Mark-up Language (GDML) was developed. Geant4 and ROOT can read and write GDML format and it is commonly
used as an exchange format for Geant4 geometries. 
\begin{table}[hbt!]
\centering
\begin{tabular}{|l|l|l|} \hline
GDML tag 		&  Child tags				& pyg4ometry class 				\\ \hline
define 			& constant				& gdml.Constant				\\
				& variable					& gdml.Variable					\\
				& expression 				& gdml.Expression				\\
				& position					& gdml.Position					\\
				& rotation					& gdml.Rotation				\\
				& scale					& gdml.Scale					\\
				& matrix					& gdml.Matrix					\\
materials 			& element					& geant4.Element				\\
				& isotope					& geant4.Isotope				\\
				& material					& geant4.Material				\\
solid  			& box					& geant4.solid.Box				\\
	  			& tube					&							\\
	  			& cutTube					&							\\
	  			& cone					&							\\
	  			& para					&							\\
	  			& trd						&							\\
	  			& trap					&							\\
	  			& sphere					&							\\
	  			& orb					&							\\
	  			& torus					&							\\
	  			& polycone				&							\\
	  			& genericPolycone			&							\\
	  			& polyhedra				&							\\
	  			& eltube					&							\\
	  			& ellipsoid					&							\\
	  			& elcone					&							\\
				& paraboloid				&							\\
				& hype					& 							\\
				& tet						& 							\\
				& xtru					& 							\\
				& twistedbox				& 							\\
				& twistedtrap				& 							\\
				& twistedtrd				& 							\\
				& twistedtube				& 							\\
				& arb8					& 							\\
				& tesselated				& 							\\
				& union					& 							\\
				& subtraction				& 							\\
				& intersection				& 							\\
				& multiUnion				& 							\\				
	  			& opticalsurface			&							\\
structure			& volume					& geant4.LogicalVolume			\\
				& physvol					& geant4.PhysicalVolume			\\ 
				& replicavol				& geant4.ReplicaVolume			\\ 
				& paravol					& geant4.ParameterisedVolume	\\ 
				& divisionvol				& geant4.DivisionVolume			\\
				& skinsurface				& geant4.SkinSurface			\\ 
				& bordersurface			& geant4.BorderSurface			\\ \hline

\end{tabular}
\caption{GDML tags and corresponding pyg4ometry classes.}
\end{table}

\section{pyg4ometry design and layout}
The core of {\em pyg4ometry} consists of python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
The constructors of the python classes are kept as close to the original Geant4 C++ implementation so that {\it pyg4ometry} users do not have to learn 
a new API. Geometry construction in python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
should be able to start creating geometry in pyg4ometry immediately. In the following sections novel or important developments in {\it pyg4ometry} are described.

@@

\subsection{Visualisation}
A  geometry hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 volume hierarchy is sufficient 
to place the meshes associated with each physical volume. A daughter volume is placed within a logical volume with a rotation $\mathbf{R}$, scale $\mathbf{S}$ and 
translation $\mathbf{T}$.

\begin{eqnarray}
\mathbf{M}	  	& = & \mathbf{M}_p \mathbf{M}_d  = \mathbf{S}_p \mathbf{R}_p  \mathbf{S}_d \mathbf{R}_d\\
\mathbf{T}	 		& = & \mathbf{M}_p \mathbf{T}_d + \mathbf{T}_p= \mathbf{S}_p \mathbf{R}_p \mathbf{T}_d + \mathbf{T}_p,
\end{eqnarray}
where the subscript $p$ indicates parent volume and $d$ indicates daughter volume.

The python version of Geant4's physical volume is also used to store visualisation attributes like the solids 
color, surface or wireframe representation and visibility. Overlaps detected in the discretised mesh geometry can be displayed separately to allow a user to remove
the potential overlaps. This is dependent on the accuracy of the mesh generated and is a particular problem with meshes based on curved surfaces.
